Pillar 1 - Sequential Pattern Mining

### 2019-03-12 Pillar 1 - Sequential Pattern Mining.Rmd
Create d_transcript_augmented in set up section for simplicity

```{r helper function}
# helper function
join_d_course     <- function(df) df %>% left_join(d_course    , by = c("Course ID")) # left_join to keep all courses present in d_transcript
join_d_transcript <- function(df) df %>% right_join(d_transcript, by = c("Course ID")) # right_joint to keep all courses present in d_transcript

@@

@@

d_transactions$taken_PF_HL <- d_course %>%

  # Exclude courses taken by majority of students (uninformative)
  filter(
    Type != "Mandatory",
    ! Letters %in% c("SKI", "PRO", "SAS", "SAH", "SAC")
    ) %>%

  # Join with transcripts
  select(- Period) %>% # remove Period to avoid duplicates
  join_d_transcript %>%

>>>>

```{r helper function}
# helper function
join_d_course     <- function(df) df %>% left_join(d_course, by = c("Course ID"))

@@

```{r d_course_informative}
d_transcript_augmented <- d_transcript %>%

  join_d_course %>%

  # Exclude courses taken by majority of students (uninformative)
  filter(
    Type != "Mandatory",
    ! Letters %in% c("SKI", "PRO", "SAS", "SAH", "SAC")
    )
```

@@

d_transactions$taken_PF_HL <- d_transcript_augmented %>%
